---
title: "<b>Scaling-up soil quality assessments:</b><br> efficient infrared-spectroscopic workflows<br> across space and time"
subtitle: "PhD defense"  
author: 
  - "Philipp Baumann"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer-mod.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
colors = c(
  blue = "#7982F7FF",
  red = "#f34213",
  purple = "#3e2f5b",
  orange = "#ff8811",
  green = "#136f63",
  white = "#FFFFFF"
)
style_mono_accent(
  base_color = "#1c5253",
  header_font_google = google_font("Arvo"),
  text_font_google   = google_font("Open Sans"),
  code_font_google   = google_font("Fira Mono"),
  colors = colors,
  title_slide_background_color = "#DABE69FF",
  title_slide_text_color = "black",
  header_h1_font_size = "1.5rem",
  header_h2_font_size = "1.25rem",
  header_h3_font_size = "1rem",
)
```


---
class: inverse-blue center middle

# Introduction

---

# .blue[Introduction]

Ay now it is **.red[time]**

---

# **Chapter 1:** Estimation of soil properties with mid-infrared soil spectroscopy across yam production landscapes in West Africa

.left-column[
**.blue[ Background: ]**
<br>
<br>
<br>
<br>
**.lgreen[Aims:]**
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
** .red[ Main objectives and research questions: ] **
]

.right-column[
- Increasing **land use frequencies** and **shorter fallow periods** in the **"yam belt" of West Africa**
- Importance of **soil organic matter** for soil quality: 
  - storage capacity and availability of essential plant nutrients
<br>


- Provide a tool to **rapidly identify** and understand soil fertility constraints to yam production for new soils in the project regions:
  - .e.g., to better derive **site-specific** nutrient recommendations for yam in **four different** yam-growing **soil ecoregions** in Ivory Coast and Burkina Faso (timing, placement, form of fertilizer)
  - **cover the typical variation** in soil properties for yam-growing areas:  soils from 80 fields of smallholder farmers; climatic gradient between humid forest and northern Guinean savanna
  - verify the soil quality effects of sustainable and innovative soil and crop management options


- **Develop and assess mid-IR spectroscopy models** to estimate soil properties that describe inherent soil fertility and control nutrient availability.
- What is the **potential** and what are the the **limitations** of **spectroscopic soil diagnostics** for discriminating landscape level and farm specific soil variability for agronomic purposes?
]
